---
title: "Biden Polling"
author: Naveed Ahmad
format: html
execute: 
  cache: false
---


```{r}
#| message: false
suppressPackageStartupMessages(library(tidyverse))
library(tidymodels)
library(broom)
poll_data <- tibble(biden = as.factor(c(rep("Yes", 655), 
                                        rep("No", 904)))) |> 
                slice_sample(prop = 1)
           
```

```{r}
#| cache: true
fit_biden <- logistic_reg() |> 
  fit(biden ~ 1, data = poll_data)
  
```

```{r}
library(gt)
library(dplyr)
library(marginaleffects)
tidy(fit_biden, conf.int = TRUE) %>%
  select(term, estimate, conf.low, conf.high) %>%
  gt() %>%
  fmt_number(
    columns = c(estimate, conf.low, conf.high),
    decimals = 3
  ) %>%
  cols_label(
    term = "Term",
    estimate = "Estimate",
    conf.low = "Lower CI",
    conf.high = "Upper CI"
  ) %>%
  tab_header(
    title = "Model Estimates with 95% Confidence Intervals"
  )
```

```{r}
biden_vote <- data.frame(
  estimate = 0.42,
  conf.low = 0.395,
  conf.high = 0.445
)
```
```{r}
biden_vote <- avg_predictions(fit_biden, type = "prob")
ggplot(biden_vote, aes(x = 1, y = estimate)) +
  geom_point(size = 4, color = "navy") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.1, color = "navy") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0.38, 0.46)) +
  theme_minimal(base_size = 14) +
  theme(
    axis.title = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    plot.caption = element_text(hjust = 1)
  ) +
  labs(
    title = "Support for President Biden in March 2024",
    subtitle = "42% is not a good sign for an incumbent seeking reelection",
    caption = "Source: YouGov poll, March 2024."
  )
```

## Model Structure

The general form of our regression model is:

Our model will predict outcome of voters in favor of Biden in general elections however, our model is based upon some assumptions and predictions are expected to show the possible results.
The data for this study is collected from 1559 individual voters in the month of August 2024, from twelve states of USA .
$$
Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \cdots + \beta_k X_k + \varepsilon
$$

Public surveys provide valuable insight about general elections however, voters response at poll stations may be very due to election companign and speeches of contesting candidates. 



$$
\text{logit}(\hat{p}) = -0.3222
$$

$$
\hat{p} = \frac{1}{1 + e^{-(-0.3222)}} \approx 0.4203
$$

We have adopted the logistic regression model because our outcome variable was binary i.e yes (1) and No (0) with 95% confidence interval. 

The prediction shows that there are 42% chances with confidence level of 95% that a voter will cast vote in favor of Joe Biden in general election 2024.
